---
title: "contribution"
output: html_notebook
---

```{r setup}
library(readxl)
xlM <- read_excel("Book4.xlsx", range = "a10:a46")
xlF <- read_excel("Book4.xlsx", range = "b10:b34")

dfM = c(xlM$Male)
dfF = c(xlF$Female)
```

## 2. assuming non equal variance, use 2 samples T test with non equal variances
### assumption
H0: variance of male and variance of female is equal.  
H1: not H0.  
significant level: 5%  

```{r}
var.test(dfM, dfF)
```
P (0.08738) is greater than 5%.  H0 is not rejected.  

### assumption
H0: mean of male and mean of female is equal.  
H1: not H0.  
significant level: 5%  

```{r}
t.test(dfM, dfF)
```
P (0.002825) is less than 5%.  H0 is rejected.

### assumption
H0: mean of male and mean of female is equal.  
H1: mean of male is larger than mean of female.  
significant level: 5%  

```{r}
t.test(dfM, dfF, alternative = "greater")
```
P (0.001412) is less than 5%.  H0 is rejected.

### assumption
H0: mean of male and mean of female is equal.  
H1: mean of male is smaller than mean of female.  
significant level: 5%  

```{r}
t.test(dfM, dfF, alternative = "less")
```
P (0.9986) is greater than 5%.  H0 is not rejected.

## conclusion
mean of bonus for male is larger than female one.